Model Fitting

### 2017-08-08 model_fitting.Rmd
finished comparing results to stack overflow model, continued with model fitting, added interactions, updated hours

library(stringr)
library(rebus)
library(survival) 
```

```{r, include = FALSE}
#function to get AIC statistics
get_aic <- function(cr_obj, num_parameters, data) {
  aic <- (-2*cr_obj$loglik[2]) + (2*num_parameters)
  return(aic)
}

@@

#posting times
x$post_datetime <- as.POSIXct(x$post_date,origin="1970-01-01")
x$post_d <- format(x$post_datetime, "%m/%d/%y")
x$post_time <- format(x$post_datetime, " %H:%M:%S")
x$post_weekday <- factor(weekdays(x$post_datetime), levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
x$post_hour <- as.numeric(format(x$post_datetime,"%H"))

x$post_ampm <- "Night"
x$post_ampm[x$post_hour >= 5 & x$post_hour < 12] <- "Morning"
x$post_ampm[x$post_hour >= 12 & x$post_hour < 17] <- "Afternoon" #noon - 5pm 
x$postampm[x$post_hour >= 17 & x$post_hour < 20] <- "Evening" #5pm - 8pm

#whether or not it was cateogorized correctly
x$categorized <- 0
x$categorized[!is.na(x$category)] <- 1

@@

#if text contains end punctuation
x$contain_punct <- FALSE
x$contain_punct[!is.na(x$text_till_punct)] <- TRUE

@@

#matrix of tags (splitting up tags variable wherever there's a comma)
split_tags <- str_split(x$tags, ", ", simplify = TRUE)

#character vector of all tags (empty strings removed)
tag_vector <- as.vector(split_tags)
tag_vector <- tag_vector[which(tag_vector != "")]

unique_tags <- unique(tag_vector)

@@

@@

```{r, echo = FALSE}
cr1 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
                  as.factor(n_tags) + as.factor(pic_included) + text_length + title_length + 
                  device_length + post_weekday + as.factor(post_hour) + text_till_punct + 
                  text_end_punct + title_questionmark + title_begin_wh + 
                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
                  greeting + update + avg_tag_length + max_tagwords + avg_tag_score + 
                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
                  newline_ratio, data = x)
s <- summary(cr1)
s$rsq
get_aic(cr1, 72, data = x) #83471.68
get_rsq_adj(cr1, 72) #0.00513921

#removed greeting and text_end punct (p-values > .8)
cr2 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
                  as.factor(n_tags) + as.factor(pic_included) + text_length + title_length + 
                  device_length + post_weekday + as.factor(post_hour) + text_till_punct + 
                  title_questionmark + title_begin_wh + 
                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
                  update + avg_tag_length + max_tagwords + avg_tag_score + 
                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
                  newline_ratio, data = x)
summary(cr2)
get_aic(cr2, 70, data = x) #83467.71
get_rsq_adj(cr2, 70) #0.005397121

#removed max_tagwords
cr3 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
                  as.factor(n_tags) + as.factor(pic_included) + text_length + title_length + 
                  device_length + post_weekday + as.factor(post_hour) + text_till_punct + 
                  title_questionmark + title_begin_wh + 
                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
                  update + avg_tag_length + avg_tag_score + 
                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
                  newline_ratio, data = x)
summary(cr3)
get_aic(cr3, 69, data = x) #83465.91
get_rsq_adj(cr3, 69) #0.005520927

#removed avg_tag_length
cr4 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
                  as.factor(n_tags) + as.factor(pic_included) + text_length + title_length + 
                  device_length + post_weekday + as.factor(post_hour) + text_till_punct + 
                  title_questionmark + title_begin_wh + 
                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
                  update + avg_tag_score + 
                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
                  newline_ratio, data = x)
summary(cr4)
get_aic(cr4, 68, data = x) #83463.95
get_rsq_adj(cr4, 68) #0.005649183

#removed text_till_punct
cr5 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
                  as.factor(n_tags) + as.factor(pic_included) + text_length + title_length + 
                  device_length + post_weekday + as.factor(post_hour) + 
                  title_questionmark + title_begin_wh + 
                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
                  update + avg_tag_score + 
                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
                  newline_ratio, data = x)
summary(cr5)
get_aic(cr5, 67, data = x) #83462.4
get_rsq_adj(cr5, 67) #0.005766099

#removing n_tags
cr6 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
                  as.factor(pic_included) + text_length + title_length + 
                  device_length + post_weekday + as.factor(post_hour) + 
                  title_questionmark + title_begin_wh + 
                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
                  update + avg_tag_score + 
                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
                  newline_ratio, data = x)
summary(cr6)
get_aic(cr6, 63, data = x) # 83455.8
get_rsq_adj(cr6, 63) #0.00624444

#remove text_length
cr7 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
                  as.factor(pic_included) + title_length + 
                  device_length + post_weekday + as.factor(post_hour) + 
                  title_questionmark + title_begin_wh + 
                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
                  update + avg_tag_score + 
                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
                  newline_ratio, data = x)
summary(cr7)
get_aic(cr7, 62, data = x) #83455.28
get_rsq_adj(cr7, 62) #0.006333204

#remove title_length
cr8 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
                  as.factor(pic_included) + 
                  device_length + post_weekday + as.factor(post_hour) + 
                  title_questionmark + title_begin_wh + 
                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
                  update + avg_tag_score + 
                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
                  newline_ratio, data = x)
summary(cr8)
get_aic(cr8, 61, data = x) #83454.54
get_rsq_adj(cr8, 61) #0.006427927

#remove pic_included
cr9 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
                  device_length + post_weekday + as.factor(post_hour) + 
                  title_questionmark + title_begin_wh + 
                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
                  update + avg_tag_score + 
                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
                  newline_ratio, data = x)
summary(cr9)
get_aic(cr9, 60, data = x) #83454.3
get_rsq_adj(cr9, 60) #0.0065088

#remove prior_effort
cr10 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
                  device_length + post_weekday + as.factor(post_hour) + 
                  title_questionmark + title_begin_wh + 
                  capital_title + capital_text + text_all_lower + gratitude + 
                  update + avg_tag_score + 
                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
                  newline_ratio, data = x)
summary(cr10)
get_aic(cr10, 59, data = x) #83454.39 aic went up 
get_rsq_adj(cr10, 59) #0.00658092

>>>>

library(stringr)
library(rebus)
library(survival) 
library(stats)
```

```{r, include = FALSE}

@@

#posting times
x$post_datetime <- as.POSIXct(x$post_date,origin="1970-01-01")
x$post_weekday <- factor(weekdays(x$post_datetime), levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
x$post_hour <- as.numeric(format(x$post_datetime,"%H"))

x$post_ampm <- "Night"
x$post_ampm[x$post_hour >= 5 & x$post_hour < 12] <- "Morning"
x$post_ampm[x$post_hour >= 12 & x$post_hour < 17] <- "Afternoon" #noon - 5pm 
x$post_ampm[x$post_hour >= 17 & x$post_hour < 20] <- "Evening" #5pm - 8pm

@@

#if text contains end punctuation
x$text_contain_punct <- FALSE
x$text_contain_punct[!is.na(x$text_till_punct)] <- TRUE

@@

#matrix of tags (splitting up tags variable wherever there's a comma)
split_tags <- str_split(x$tags, ", ", simplify = TRUE)
#character vector of all tags (empty strings removed)
tag_vector <- as.vector(split_tags)
tag_vector <- tag_vector[which(tag_vector != "")]
unique_tags <- unique(tag_vector)

@@

#number of "popular" tags a question contains
#setting threshold to define popular tags: tag must occur 0.5% of the time to be considered "popular"
threshold <- 0.005
#function that sets num_pop to 1 if the tag is considered popular, 0 if not
num_pop <- function(var, threshold) {
  num_pop <- rep(0, nrow(x))
  num_pop[x[[var]] >= threshold] <- 1
  return(num_pop)
}
numpop1 <- num_pop("score1", threshold)
numpop2 <- num_pop("score2", threshold)
numpop3 <- num_pop("score3", threshold)
numpop4 <- num_pop("score4", threshold)
#finding the total number of popular tags for a question
x$num_pop_tags <- numpop1 + numpop2 + numpop3 + numpop4

x$is_weekend <- FALSE
x$is_weekend[x$post_weekday == "Saturday" | x$post_weekday == "Sunday"] <- TRUE

@@

```{r, echo = FALSE}
cr1 <- coxph(Surv(time_until_answer, answered) ~ category + title_length + text_length + device_length + as.factor(n_tags) + as.factor(pic_included) + new_user + post_weekday + post_ampm + contain_unanswered + contain_answered + avg_tag_length + avg_tag_score + num_pop_tags + text_till_punct + title_questionmark + title_begin_wh + capital_text + capital_title + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio, data = x)

summary(cr1)
library(stats) #to get AIC
AIC(cr1, k = 2) #83451.51
```
* fit model text_end_punct, compared AIC to that of model containing text_till_punct (text_till_punct had lower AIC)
* fit model with max_tagwords instead of avg_tag_length (avg_tag_length had lower) 
* fit model with post_hour instead of post_ampm (post_ampm had lower)
* fit model with is_weekend instead of post_weekend (post_weekday lower)
* fit with num_prior_effort, prior_effort is lower
* fit with n_images instead of pic_included, n_images is better
* fit with tag_included instead of n_tags, tag_included is better

```{r, echo = FALSE}
#the new full model (best combination of all variables) 
cr2 <- coxph(Surv(time_until_answer, answered) ~ category + title_length + text_length + 
                 device_length + as.factor(tag_included) + n_images + new_user + post_weekday + 
                 post_ampm + contain_unanswered + contain_answered + avg_tag_length + avg_tag_score + 
                 num_pop_tags + text_till_punct + title_questionmark + title_begin_wh + capital_text + 
                 capital_title + text_all_lower + prior_effort + gratitude + greeting + update + 
                 newline_ratio, data = x)
AIC(cr2, k = 2) #83445.74
summary(cr2)
```

```{r, echo = FALSE}
#remove avg_tag_length
cr3 <- coxph(Surv(time_until_answer, answered) ~ category + title_length + text_length + 
                 device_length + as.factor(tag_included) + n_images + new_user + post_weekday + 
                 post_ampm + contain_unanswered + contain_answered + avg_tag_score + 
                 num_pop_tags + text_till_punct + title_questionmark + title_begin_wh + capital_text + 
                 capital_title + text_all_lower + prior_effort + gratitude + greeting + update + 
                 newline_ratio, data = x)
AIC(cr3, k = 2) #83443.75
summary(cr3)
```

```{r, echo = FALSE}
#remove greeting
cr4 <- coxph(Surv(time_until_answer, answered) ~ category + title_length + text_length + 
                 device_length + as.factor(tag_included) + n_images + new_user + post_weekday + 
                 post_ampm + contain_unanswered + contain_answered + avg_tag_score + 
                 num_pop_tags + text_till_punct + title_questionmark + title_begin_wh + capital_text + 
                 capital_title + text_all_lower + prior_effort + gratitude + update + 
                 newline_ratio, data = x)
AIC(cr4, k = 2) #83441.81
summary(cr4)
```

```{r, echo = FALSE}
#remove gratitude
cr5 <- coxph(Surv(time_until_answer, answered) ~ category + title_length + text_length + 
                 device_length + as.factor(tag_included) + n_images + new_user + post_weekday + 
                 post_ampm + contain_unanswered + contain_answered + avg_tag_score + 
                 num_pop_tags + text_till_punct + title_questionmark + title_begin_wh + capital_text + 
                 capital_title + text_all_lower + prior_effort + update + 
                 newline_ratio, data = x)
AIC(cr5, k = 2) #83439.96
summary(cr5)
```

```{r, echo = FALSE}
#remove text_till_punct
cr6 <- coxph(Surv(time_until_answer, answered) ~ category + title_length + text_length + 
                 device_length + as.factor(tag_included) + n_images + new_user + post_weekday + 
                 post_ampm + contain_unanswered + contain_answered + avg_tag_score + 
                 num_pop_tags + title_questionmark + title_begin_wh + capital_text + 
                 capital_title + text_all_lower + prior_effort + update + 
                 newline_ratio, data = x)
AIC(cr6, k = 2) #83448.41
summary(cr6)
```

```{r, echo = FALSE}
#remove num_pop_tags
cr7 <- coxph(Surv(time_until_answer, answered) ~ category + title_length + text_length + 
                 device_length + as.factor(tag_included) + n_images + new_user + post_weekday + 
                 post_ampm + contain_unanswered + contain_answered + avg_tag_score + 
                 title_questionmark + title_begin_wh + capital_text + 
                 capital_title + text_all_lower + prior_effort + update + 
                 newline_ratio, data = x)
AIC(cr7, k = 2) #83437.22
summary(cr7)
```

```{r, echo = FALSE}
#remove title_length 
cr8 <- coxph(Surv(time_until_answer, answered) ~ category + text_length + 
                 device_length + as.factor(tag_included) + n_images + new_user + post_weekday + 
                 post_ampm + contain_unanswered + contain_answered + avg_tag_score + 
                 title_questionmark + title_begin_wh + capital_text + 
                 capital_title + text_all_lower + prior_effort + update + 
                 newline_ratio, data = x)
AIC(cr8, k = 2) #83436.49
summary(cr8)
```

```{r, echo = FALSE}
#remove text_length 
cr9 <- coxph(Surv(time_until_answer, answered) ~ category + 
                 device_length + as.factor(tag_included) + n_images + new_user + post_weekday + 
                 post_ampm + contain_unanswered + contain_answered + avg_tag_score + 
                 title_questionmark + title_begin_wh + capital_text + 
                 capital_title + text_all_lower + prior_effort + update + 
                 newline_ratio, data = x)
AIC(cr9, k = 2) #83435.68
summary(cr9)
```

```{r, echo = FALSE}
#remove tag_included 
cr10 <- coxph(Surv(time_until_answer, answered) ~ category + 
                 device_length + n_images + new_user + post_weekday + 
                 post_ampm + contain_unanswered + contain_answered + avg_tag_score + 
                 title_questionmark + title_begin_wh + capital_text + 
                 capital_title + text_all_lower + prior_effort + update + 
                 newline_ratio, data = x)
AIC(cr10, k = 2) #83435.13
summary(cr10)
```

* next variable I would remove would be n_images, but doing this increases the AIC, removing any other variable increases the AIC
* also need to think about if want to keep contain_answered and contain_unanswered (is there an issue with the category var)

```{r, include = FALSE}
#function to compare nested models 
compare_nested <- function(crfull, crreduced, param_full, param_reduced) {
  like_f <- crfull[[loglik]]
  like_r <- crreduced[[loglik]]
  stat <- 2*(like_f - like_r)
}
```

```{r, echo = FALSE}
#added interaction between title_questionmark and title_begin_wh
cr11 <- coxph(Surv(time_until_answer, answered) ~ category + 
                 device_length + n_images + new_user + post_weekday + 
                 post_ampm + contain_unanswered + contain_answered + avg_tag_score + 
                 title_questionmark + title_begin_wh + capital_text + 
                 capital_title + text_all_lower + prior_effort + update + 
                 newline_ratio + title_questionmark*title_begin_wh, data = x)
AIC(cr11, k = 2) #83429.68
summary(cr11)
```

```{r, echo = FALSE}
#added interaction between new_user and update
cr12 <- coxph(Surv(time_until_answer, answered) ~ category + 
                 device_length + n_images + new_user + post_weekday + 
                 post_ampm + contain_unanswered + contain_answered + avg_tag_score + 
                 title_questionmark + title_begin_wh + capital_text + 
                 capital_title + text_all_lower + prior_effort + update + 
                 newline_ratio + title_questionmark*title_begin_wh + new_user*update, data = x)
AIC(cr12, k = 2) #83425.59
summary(cr12)
```

```{r, echo = FALSE}
#added interaction between new_user and newline_ratio
cr13 <- coxph(Surv(time_until_answer, answered) ~ category + 
                 device_length + n_images + new_user + post_weekday + 
                 post_ampm + contain_unanswered + contain_answered + avg_tag_score + 
                 title_questionmark + title_begin_wh + capital_text + 
                 capital_title + text_all_lower + prior_effort + update + 
                 newline_ratio + title_questionmark*title_begin_wh + new_user*update + 
                 new_user*newline_ratio, data = x)
AIC(cr13, k = 2) #83422.18
summary(cr13)
```

```{r, echo = FALSE}
#added interaction between category and device length
cr14 <- coxph(Surv(time_until_answer, answered) ~ category + 
                 device_length + n_images + new_user + post_weekday + 
                 post_ampm + contain_unanswered + contain_answered + avg_tag_score + 
                 title_questionmark + title_begin_wh + capital_text + 
                 capital_title + text_all_lower + prior_effort + update + 
                 newline_ratio + title_questionmark*title_begin_wh + new_user*update + 
                 new_user*newline_ratio + category*device_length, data = x)
AIC(cr14, k = 2) #83335.8
summary(cr14)
```
